Autogenerated Questions Paper Draft

### 2018-05-06 paper_draft/paper_draft.tex
Add distractor examples for Functions

\begin{VerbCM}
Given the following function definition:
\end{VerbCM}
\begin{lstlisting}
int Pow() 
{ 
	return 4.5 + 1.0; 
}
\end{lstlisting}
\begin{VerbCM}
What is printed from the following call? 
\end{VerbCM}
\begin{lstlisting}[caption={\textbf{Functions} Difficulty 1 Example}, label=lst-functions_1]
cout << Pow() << endl; 
\end{lstlisting}

@@

This next difficulty is in the same vain as Difficulty 1, except it focuses on data types of parameters instead of the return type. This way, students are tested more on knowledge on parameter passing and type coercion, as well as the operations that result from them.
Because of the similar objective of the two difficulties, a format that resembles Difficulty 1 is used here as well.
\hfill \par \hfill \par

\noindent
\begin{VerbCM}
Given the following function definition:
\end{VerbCM}
\begin{lstlisting}
float Switch(float a, int b)
{
    return a - b;
}
\end{lstlisting}
\begin{VerbCM}
What is printed from the following call?
\end{VerbCM}
\begin{lstlisting}[caption={\textbf{Functions} Difficulty 2 Example}, label=lst-functions_2]
cout << Switch(3.5, 1.5) << endl;
\end{lstlisting}

@@

\begin{lstlisting}[caption={\textbf{Functions} Difficulty 3 Example}, label=lst-functions_3, float]
Given the following function definition:
void Calculate(int& a, int& b, int c)
{
	b = a / b + c;
}

What value is printed after the following statements?
int marks = 5;
int matrix = 4;
int item = 5;
Calculate(marks, matrix, item);
cout << matrix << endl;
\end{lstlisting}

@@

Because this question depends on the expression inside the function, some of the same distractor methods are used within this category, such as disregarding order of operations and
using float values and float operations. The novel distractor methods are much more interesting.
The first (and most obvious method) distractor being equal to the original value of the variable -- if the parameter is pass-by-reference -- or the value of the expression -- if the parameter is pass-by-value. A fairly straightforward method, but effective in testing the objective of this question. 
The next distractor is simply the value of the variable declared after the printed variable (in the example above, this would be item). This method is not as particularly sophisticated, but serves as an obvious wrong answer for knowledgeable students.

>>>>

\begin{lstlisting}[caption={\textbf{Functions} Difficulty 1 GIFT Example}, label=lst-functions_1]
Given the following function definition:
int Pow() 
\{ 
	return 4.5 - 1.0; 
\}
What is printed from the following call? 
cout << Pow() << endl;
{
	=3
	~-3.5
	~3.5
	~Run-time Error
	~Compile-time Error
} 
\end{lstlisting}

@@

This next difficulty is in the same vain as Difficulty 1, except it focuses on data types of parameters instead of the return type. This way, students are tested more on knowledge on parameter passing and type coercion, as well as the operations that result from them.
Because of the similar objective of the two difficulties, a format that resembles Difficulty 1 is used here as well.

\begin{lstlisting}[caption={\textbf{Functions} Difficulty 2 GIFT Example}, label=lst-functions_2, float]
Given the following function definition:
float Switch(int a, int b)
\{
    return a / b;
\}
What is printed from the following call?
cout << Switch(5.5, 4.5) << endl;
{
	=1
	~1.25
	~1.222
	~1.5
}
\end{lstlisting}

@@

\begin{lstlisting}[caption={\textbf{Functions} Difficulty 3 GIFT Example}, label=lst-functions_3, float]
Given the following function definition:
void Calculate(int& a, int& b, int c)
\{
	b = a + b / c;
\}

What value is printed after the following statements?
int marks = 2;
int matrix = 4;
int item = 5;
Calculate(marks, matrix, item);
cout << matrix << endl;
{
	=2
	~4
	~5
	~1
	~2.8
}
\end{lstlisting}

@@

Because this question depends on the expression inside the function, some of the same distractor methods are used within this category, such as disregarding order of operations and
using float values and float operations. The novel distractor methods are much more interesting.
The first (and most obvious method) distractor being equal to the original value of the variable -- if the parameter is pass-by-reference -- or the value of the expression -- if the parameter is pass-by-value; a fairly straightforward method, but effective in testing the objective of this question. 
The next distractor is simply the value of the variable declared after the printed variable (in the example above, this would be item). This method is not as particularly sophisticated, but serves as an obvious wrong answer for knowledgeable students.
